Proof-Reconstruction in Type Theory for Propositional Logic

### 2017-10-22 paper/sections/proof-reconstruction.tex
[ paper ] table added.

\subsubsection*{An  example.}
Let us consider the following example to exhibit the bounded technique
mentioned above for the \fuh function presented in the proposed version
for the \Metis \strip inference.

@@

@@

>>>>

\begin{example}
\label{ex:structural-recursion}

Let us consider the following example to exhibit the bounded technique
mentioned above for the \fuh function presented in the proposed version
for the \Metis \strip inference.

@@

\end{example}

@@

\begin{table}[!ht]
  \begin{center}
  {\renewcommand{\arraystretch}{1.6}%
    \begin{tabular}{|@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}l@{\hspace{2mm}}|}
    \hline
    \textbf{\Metis rule} & \textbf{Purpose} &\textbf{Theorem}\\ \hline
    \texttt{canonicalize}
      &Normalization of the formula
      &Thm.~\ref{thm:canonicalizeThm}
    \\
    \texttt{clausify}
      &Performs clausification
      &Thm.~\ref{thm:clausifyThm}
    \\
    \hyperlink{atp-conjunct}{\texttt{conjunct}}
      &Takes a formula from a conjunction
      &Thm.~\ref{thm:conjunctThm}
    \\
    \texttt{negate}
      &Negate the formula
      &Thm.~\ref{thm:negateThm}
    \\
    \texttt{resolve}
      &A general form of the resolution theorem
      &Thm.~\ref{thm:resolveThm}
    \\
    \texttt{simplify}
      &Simplify definitions and theorems
      &Thm.~\ref{thm:simplifyThm}
    \\
    \texttt{strip}
      &Strip a goal into subgoals
      &Thm.~\ref{thm:stripThm}
    \\[1ex]
    \hline
    \end{tabular}}
  \end{center}
\label{tab:agda-metis-table}
\end{table}
% ------------------------------------------------------------------------------
